Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-08-18 longSC.tex
with Constantin

The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig~\ref{fig:Figure_A5}a and Fig~\ref{fig:Figure_A5}b, respectively. The ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig~\ref{fig:Figure_A5}c. We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and default AMPT models, the ${\chi}^2$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$). This can be explained by the fact that the individual flow harmonics $v_n$ are not well described by those models compared to the event-by-event EKRT+viscous hydrodynamics. This is quantified in Fig.~\ref{fig:Figure_A5}c, showing that the ${\chi}^2$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
The default AMPT model gives best ${\chi}^2$ values for NSC($m$,$n$), especially for NSC(3,2). However the ${\chi}^2$ values of this model are worst for $v_n$ among the models and noticeably larger for $v_2$.

>>>>

The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig.~\ref{fig:Figure_A5}a and \ref{fig:Figure_A5}b, respectively. The ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig.~\ref{fig:Figure_A5}c. We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and default AMPT models, the ${\chi}^2$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$). This can be explained by the fact that the individual flow harmonics $v_n$ are not well described by those models compared to event-by-event EKRT+viscous hydrodynamics. This is quantified in Fig.~\ref{fig:Figure_A5}c, showing that the ${\chi}^2$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
The default AMPT model gives best ${\chi}^2$ values for NSC($m$,$n$), especially for NSC(3,2). However the ${\chi}^2$ values of this model are worst for $v_n$ among the models and noticeably larger for $v_2$.
